Ladies' figure skating in the 2002 Winter Olympics

### 2025-03-02 inst/skating.Rmd
extraction

Object `skating_table` is an order table.  It is structured so that
each competitor is a row, and each judge is a column.  Function
`rank_likelihood()` considers each row to be a race [or a judge], so
we need to take a transpose.  The following R idiom is plausible but
**incorrect**:

```{r,skatingwrong}
skating_incorrect <- rank_likelihood(t(skating_table)) # incorrect
```

The above is incorrect because we are applying a rank technique to an
order table.  Correct analysis follows.  One good thing to do is to
present the dataset as an order table;

```{r,coercetoranktable}
ordertable_to_ranktable(skating_table)
```

@@

```{r justtop7}
skating_table
o <- ordertable_to_ranktable(skating_table)
o
```

```{r setclasstomatrix}
class(o) <- "matrix"
o
```

Select just the top seven:
```{r selectthetop7}
o <- o[,1:7]
o
```

and now replace ranks with internal ranks (that is, rank among the top
seven):

```{r replaceranks}
o <- t(apply(o,1,rank))
colnames(o) <- rownames(skating_table)[1:7]
o
```

Now coece to a `ranktable`:

```{r coercetoranktble}
class(o) <- "ranktable"
o
```

Thence to an order table:

```{r thenceto}
o <- ranktable_to_ordertable(o)
o
```

>>>>

Object `skating_table` is an order table.  It is structured so that
each competitor is a row, and each judge is a column.  One good thing
to do is to present the dataset as an order table;

```{r,coercetoranktable}
as.ranktable(skating_table)
```

@@

Now we consider only the top seven competitors (that is, the top seven
according to Judge 1).

```{r justtop7}
(o <- skating_table[1:7])
```

```{r thenceto}
(o <- as.ranktable(o))
```
